An Empirical Analysis of the Role of Energy in Economic Growth

### 2013-04-15 EconGrowth.Rnw
Adjusted to-do list.

\item{Heun: Rearrange the panels on the CD gamma grid search graph}
\item{Heun: Change the strip to transparent on the CD gamma grid search graph}
\item{Heun: Get full country names into the CD gamma grid search graph}

@@

\item{Heun: Change the presentation to use the cdeGridLattice function instead of cdeGridGraph}
\item{Heun: Remove cdeGridGraph function}

@@

@@

<<Historical_Lattice_Graph, fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.pos="H", fig.cap="Historical data. Indexed GDP ($y$), capital stock ($k$), labor ($l$), thermal energy ($q$), exergy ($x$), and useful work ($u$).">>=
createHistoricalLatticeGraph()
@

>>>>

@@

@@

\item{\st{Heun: Rearrange the panels on the CD gamma grid search graph}}
\item{\st{Heun: Change the strip to transparent on the CD gamma grid search graph}}
\item{\st{Heun: Get full country names into the CD gamma grid search graph}}
\item{\st{Heun: Change the presentation to use the cdeGridLattice function instead of cdeGridGraph}}
\item{\st{Heun: Remove cdeGridGraph function}}

@@

<<Historical_Lattice_Graph, fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.pos="H", fig.cap="Historical data: Indexed GDP ($y$), capital stock ($k$), labor ($l$), thermal energy ($q$), exergy ($x$), and useful work ($u$).">>=
createHistoricalLatticeGraph()
@
